Fourmile Calibrations and Output

### 2024-06-17 38HRU_model/fourmile_model_outputs.Rmd
update

gw <- bind_rows(
  gw_gridall, gw_statnall,
  gw_grid2011, gw_grid2012,
  gw_grid2013, gw_grid2014,
  gw_grid2015, gw_grid2016,
  gw_grid2017, gw_grid2018,
  gw_grid2019, gw_grid2020,
  gw_statn2011, gw_statn2012,
  gw_statn2013, gw_statn2014,
  gw_statn2015, gw_statn2016,
  gw_statn2017, gw_statn2018,
  gw_statn2019, gw_statn2020
) %>%
  mutate(date = mdy(time),
         year = year(date))

>>>>

gw <- bind_rows(
  gw_gridall, gw_statnall,
  # gw_grid2011, gw_grid2012,
  # gw_grid2013, gw_grid2014,
  # gw_grid2015, gw_grid2016,
  # gw_grid2017, gw_grid2018,
  # gw_grid2019, gw_grid2020,
  # gw_statn2011, gw_statn2012,
  # gw_statn2013, gw_statn2014,
  # gw_statn2015, gw_statn2016,
  # gw_statn2017, gw_statn2018,
  # gw_statn2019, gw_statn2020
) %>%
  mutate(date = mdy(time),
         year = year(date))
